---
title: "SZ_Package_Note"
author: "Sara(Yuhua) Zong"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      error = FALSE, results = "asis")
```
# Developing an R package:
1. Navigate to the desired project location with `setwd()` or use the `Create a project` 
button on the upper left hand corner of R Studio to create a new project in the desired
project location.
2. Use `devtools::create("project_name")` to create a new R project. It will create 
the following files inside the project folder:
  - .gitignore
  - .Rbuildignore
  - DESCRIPTION
  - project_name.Rproj
  - NAMESPACE
  - an R folder
3. Working on the `DESCRIPTION` file:
  - Modify `Title` and `Description` accordingly (Note: values span multiple lines
  needs four spaces indent)
  - Modify `Authors@R` with `person("first_name", "last_name", email = ..., role = c("aut", "cre"))`
  - Use `devtools::use_package("package_name")` to add package dependency to `Import:` 
  in DESCRIPTION
  - Use `devtools::use_build_ignore("note")` to modify the `.Rbuildignore` file
4. Add functions to `.R` files in the R folder:
  - `use_this::use_r("file_name")` to creat a blank `.R` file in the R folder
  - Add function documentation:
      - Title in the format of `#' @title <fxn title>`
      - Description in the format of `#' @description <fxn description>`
      - Parameter(s) in the format of `#' @param <name> <description>`
      - Output in the format of `#' @return <fxn outupt>`
      - Example of how function is called in the format of `#' @example(s) <example>`
      (Note: example will need to pass check if it's added to documentation)
      - Don't forget to `#' @export`
  - `devtools::document()` to create the nicely formatted function documentations
  - To add the ***magrittr*** pipe, use `usethis::use_pipe()`
5. Use GitHub Actions to check codes add to the repo:
  - `usethis::use_github_action_check_standard()` for standard check
  - `usethis::use_github_action_check_release()` for quick check
  - either function creates a `.github` folder, a `workflows` folder with a 
  `R-CMD-check.yaml` file inside, and a `R-CMD-check` badge will be added to the
  `README.md`

### Testing
```{r}
library(tidyverse)
library(szrtools)
print_ttest(t.test(mpg ~ am, data = mtcars))
t.test(mpg ~ am, data = mtcars)

```

